To the interested reader,
\\
\\
This document is a compilation of lecture notes taken during the Fall 2022 semester for MATH2135: Linear Algebra for Mathematics Majors at the University of Colorado Boulder. The course used \cite{andrilli2016linear} as its primary text. Supplemental texts included \cite{treil2017linear,axler2024linear,olver2006applied}. As such, many theorems, definitions, and content may be quoted or derived from the aforementioned books. This course was taught by Robin Deeley, Ph. D.
\\
\\
Appendix~\ref{appendix:a} is provided as a nonexhaustive refresher on proof techniques commonly covered in a discrete mathematics course. Appendix~\ref{appendix:a} is a result of lecture notes compiled during the Summer 2022 semester for MATH2520: Discrete Mathematics at Front Range Community College. This course was taught by Kenneth M. Monks, Ph. D. The primary text was \cite{levin2021discrete}, but \cite{hammack2018book} was also used as supplement.
\\
\\
Appendix~\ref{appendix:b} is provided as a nonexhaustive refresher on functions, as preparation for Chapter~\ref{chapter:lintrans}, the chapter on linear transformations. Appendix~\ref{appendix:b} is a result of both content covered in \cite{andrilli2016linear} and MATH2520 lecture notes.
\\
\\
Appendix~\ref{appendix:c} is provided as an introduction to numerical linear algebra, as covered by APPM4600: Numerical Methods and Scientific Computation. This course was taught by Eduardo Corona, Ph. D. There was no official course text, but in writing the section, \cite{olver2006applied} was primarily referenced. It is worth noting that this appendix is less-polished than the rest of the document.
\\
\\
Each chapter in this text has an accompanying quote, or accompanying image, from \href{https://xkcd.com/license.html}{XKCD}. These additions are tied to the content of the chapter and are meant to add lighthearted humor to the material. 
\\
\\
For quick reference, the backmatter contains a list of theorems and definitions and the page numbers on which they are on.
\\
\\
The current edition of this text consists primarily of concepts covered in MATH2135. Appendix~\ref{appendix:c} contains some exposition on numerical linear algebra. In the future, however, the author would like to add additional topics, not covered in the courses, to provide for a more complete text. Possible future topics include, but are not limited to, optimization in \(\mathbb{R}^n\) with the Hessian matrix, applications of linear algebra to differential equations, and linear programming. As MATH2135 is a proof-based course, the author will prioritize rigor in the presentation of any additional topics and will refrain from implementing sections where the necessary level of rigor has not been reached.
\\
\\
Future editions are more likely to resolve errata or reframe the discussion of existing material instead of implementing new sections entirely. By the end of MATH2135, a student will have a degree of mathematical maturity enough to make inroads into additional topics in linear algebra without direct instruction.
\pagebreak
\vphantom
\\
\\
The author would like to provide the following additional resources for students currently taking a linear algebra course:
\begin{enumerate}
    \item \href{https://www.math.brown.edu/streil/papers/LADW/LADW_2017-09-04.pdf}{Sergei Treil's \textit{Linear Algebra Done Wrong}.}
    \item \href{https://linear.axler.net/LADR4e.pdf}{Sheldon Axler's \textit{Linear Algebra Done Right}.}
    \item \href{https://youtube.com/playlist?list=PL221E2BBF13BECF6C}{Gilbert Strang's Linear Algebra Lectures From Fall 2011.}
    \item \href{https://www.youtube.com/playlist?app=desktop&list=PLZHQObOWTQDPD3MizzM2xVFitgF8hE_ab}{3Blue1Brown's \textit{Essence of Linear Algebra}.}
\end{enumerate}
While much effort has been put in to remove typos and mathematical errors, it is very likely that some errors, both small and large, are present. Please keep in mind that the author wrote this resource during his undergraduate studies. If an error needs to be resolved, please contact Adithya Bhaskara at \href{mailto:adithya@colorado.edu}{adithya@colorado.edu}.
\\
\\
Finally, the author would like to dedicate this set of lecture notes to \textit{Aidan Janney}, \textit{Erika Sj\"{o}blom}, and \textit{Tate McDonald}, three of the author's closest friends who plan to take Linear Algebra in the upcoming semester; Spring 2023, at the time of writing.
\\
\\
\rightline{Best Regards,}
\rightline{Adithya Bhaskara}
\vfill
\rightline{\textbf{REVISED: \today}}